Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-07-02 survey/survey.tex
some consistency changes in section 3.

\paragraph*{Conditionals.}
Even though \ensuremath{\Pi } lacks conditional expressions, they are
expressible using the distributivity and factoring laws. The
diagrammatic representation of \ensuremath{\dist} shows that it redirects the flow
of a value \ensuremath{v:b} based on the value of another one of type
\ensuremath{b_1+b_2}. If we choose \ensuremath{1+1} to be \ensuremath{\mathit{bool}} and apply either
\ensuremath{c_1:b\leftrightarrow b} or \ensuremath{c_2:b\leftrightarrow b} to the value \ensuremath{v}, then we essentially
have an `if' expression.

\ensuremath{\mathit{if}_{c_1,c_2} : \mathit{bool} \times b \leftrightarrow \mathit{bool} \times b}

@@

The diagram above shows the input value of type \ensuremath{(1+1)\times b} processed
by the distribute operator \ensuremath{\dist}, which converts it into a value of
type \ensuremath{(1\times b)+(1\times b)}. In the \ensuremath{\mathit{left}} branch, which corresponds to the
case when the boolean is \ensuremath{\mathit{true}} (i.e. the value was \ensuremath{\mathit{left} ~()}),
the combinator~\ensuremath{c_1} is applied to the value of type~\ensuremath{b}. The right
branch which corresponds to the boolean being \ensuremath{\mathit{false}} passes
the value of type \ensuremath{b} through the combinator \ensuremath{c_2}.

@@

The first two equivalences in Fig.~\ref{figf} reflect the basic
coherence between type-level swapping and and the level-2 combinator
actions. The next four arise because of interactions between
(additive and multiplicative) level-1 associativity and swapping.
In other words, they arise as critical pairs.  For example,
the first expresses that the two ways of going from
$\left(A \oplus B\right) \oplus C$ to $B \oplus \left(C \oplus A\right)$
are equivalent, with the second saying that the reverse (i.e.
the results of applying $!$\~) also gives equivalent programs.
The last two say the same but for the multiplicative structure.

>>>>

\paragraph*{Conditionals.}
Even though \ensuremath{\Pi } lacks conditional expressions, they are
expressible using the distributivity and factoring laws. The
diagrammatic representation of \ensuremath{\dist} shows that it redirects the flow
of a value \ensuremath{v:b} based on the value of another one of type
\ensuremath{b_1+b_2}. If we choose \ensuremath{1+1} to be
\ensuremath{\mathit{bool}} and apply either \ensuremath{c_1:b_1\leftrightarrow
b_2} or \ensuremath{c_2:b_1\leftrightarrow b_2} to the value \ensuremath{v},
then we essentially have an `if' expression.

\ensuremath{\mathit{if}_{c_1,c_2} : \mathit{bool} \times b_1 \leftrightarrow \mathit{bool} \times b_2}

@@

The diagram above shows the input value of type \ensuremath{(1+1)\times b_2}
processed by the distribute operator \ensuremath{\dist}, which converts it into
a value of type \ensuremath{(1\times b_2)+(1\times b_2)}. In the
\ensuremath{\mathit{left}} branch, which corresponds to the
case when the boolean is \ensuremath{\mathit{true}} (i.e. the value was
\ensuremath{\mathit{left} ~()}), the combinator~\ensuremath{c_1} is applied to
the value of type~\ensuremath{b_1}. The right
branch which corresponds to the boolean being \ensuremath{\mathit{false}} passes
the value of type \ensuremath{b_1} through the combinator \ensuremath{c_2}.

@@

The first two equivalences in Fig.~\ref{figf} reflect the basic
coherence between type-level swapping and and the level-2 combinator
actions. The next four arise because of interactions between
(additive and multiplicative) level-1 associativity and swapping.
In other words, they arise as critical pairs.  For example,
the first expresses that the two ways of going from
$\left(A \oplus B\right) \oplus C$ to $B \oplus \left(C \oplus A\right)$
are equivalent, with the second saying that the reverse (i.e.
the results of applying $!$\,) also gives equivalent programs.
The last two say the same but for the multiplicative structure.
